Stock enhancement undermines community stability

### 2022-01-27 rmd/supporting_info.Rmd
edit: SI

@@

# Table S7-9
## load regression tables
source(here::here("code/table_reg.R"))
j <- 6

>>>>

## Table S7 Parameter estimates of the Bayesian state space model
Median estimates of the Bayesian state space model. Site specific parameters were excluded due to the large number of parameters. Numbers in parenthesis indicate 95% credible intervals.

```{r table_s7}

# Table S7
source(here::here("code/table_ssm.R"))

kable(df_ssm, format = "markdown")

@@

# Table S8-10
## load regression tables
source(here::here("code/table_reg.R"))
j <- 7
